---
title: "1sec_audiofiles"
author: "Brian C Leavell"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Trim/append silence to ensure that audio files are each 1 second in duration

Goal: Ensure that various audio files produced from separate markdown files and pre-existing echolocation audio files are each 1 second in duration (to standardize playback of files for propagation experiment). Additionally, standardize peak intensity (normalize) of all files.

Details: 

```{r packages}
library(seewave)
library(tuneR)
```
* Audio files needed:
  + 100to10kHz_fmtone.wav
  + puretones.wav
  + CF_1.wav
  + CF_2.wav
  + FM_1.wav
  + FM_2.wav
  + Synthetic.wav

Note: the last 5 files listed above are those used in Barber et al. 2022

```{r trim_or_add_silence}
fmsweep <- readWave("100to10kHz_fmtone.wav")
duration(fmsweep) #1sec

puretones <- readWave("puretones.wav")
duration(puretones) #0.19 sec
puretones <- addsilw(puretones, at = "end", d = 0.81, output = "Wave")
duration(puretones) #1sec

cf_1 <- readWave("CF_1.wav")
duration(cf_1) 
oscillo(cf_1)
cf_1 <- cutw(cf_1, from=0, to=1, output="Wave")
duration(cf_1) 
oscillo(cf_1)

cf_2 <- readWave("CF_2.wav")
duration(cf_2) 
oscillo(cf_2)
cf_2 <- cutw(cf_2, from=0, to=1, output="Wave")
duration(cf_2) 
oscillo(cf_2)

fm_1 <- readWave("FM_1.wav")
duration(fm_1) 
oscillo(fm_1)
fm_1 <- cutw(fm_1, from=0, to=1, output="Wave")
duration(fm_1) 
oscillo(fm_1)

fm_2 <- readWave("FM_2.wav")
duration(fm_2) 
oscillo(fm_2)
fm_2 <- cutw(fm_2, from=0, to=1, output="Wave")
duration(fm_2) 
oscillo(fm_2)

synthetic <- readWave("Synthetic.wav")
duration(synthetic) 
oscillo(synthetic)
synthetic <- cutw(synthetic, from=0, to=1, output="Wave")
duration(synthetic) 
oscillo(synthetic)
```

## Normalize
``` {r normalize}
fmsweep <- normalize(fmsweep, unit = "16", rescale = TRUE)
puretones <- normalize(puretones, unit = "16", rescale = TRUE)
cf_1 <- normalize(cf_1, unit = "16", rescale = TRUE)
cf_2 <- normalize(cf_2, unit = "16", rescale = TRUE)
fm_1 <- normalize(fm_1, unit = "16", rescale = TRUE)
fm_2 <- normalize(fm_2, unit = "16", rescale = TRUE)
synthetic <- normalize(synthetic, unit = "16", rescale = TRUE)
```

## Save .wav files
``` {r save_wavs}
#final file save as .wav
savewav(fmsweep, filename = "fmsweep_1sec.wav") 
savewav(puretones, filename = "puretones_1sec.wav") 
savewav(cf_1, filename = "cf_1_1sec.wav") 
savewav(cf_2, filename = "cf_2_1sec.wav") 
savewav(fm_1, filename = "fm_1_1sec.wav") 
savewav(fm_2, filename = "fm_2_1sec.wav") 
savewav(synthetic, filename = "synthetic_1sec.wav") 
```
## References
Barber, Jesse R., et al. "Anti-bat ultrasound production in moths is globally and phylogenetically widespread." Proceedings of the National Academy of Sciences 119.25 (2022): e2117485119.