---
title: "puretones"
author: "Brian C Leavell"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating series of pure sine tones for use in ultrasonic propagation study

Goal: Generate 5 pure tones as single .wav file.

Details: This creates a series of pure (i.e. no frequency or amplitude modulation) sinusoidal tones that are based off the range of echolocation frequencies of species listed in the pdf "WesternUS_Acoustic_Table_Mar2011" by Joe Szewczak, Humboldt State University Bat Lab, June 2018. The signals include:  
10 khz (e.g. *Euderma maculatum*)
20 kHz (e.g. )
30 khz (e.g. **)
40 khz (e.g. **)
50 khz (e.g. **)
60 khz (e.g. **)
70 khz (e.g. **)
80 khz (e.g. **)
90 khz (e.g. **)
100 khz (e.g. **). 
The series begins at 10 kHz, which is near the lower end of *Euderma maculatum*'s call and ends at 100 kHz, which is near the upper end of *Myotis californicus*'s call. Each tone is is 10 ms in duration, which is within the range of call durations from the aforementioned pdf.


```{r packages}
library(seewave)
```

Create files

Settings:
Pure tones in sequence: 10 kHz, 35 kHz, 50 kHz
Sine waves
Fade-in & Fade-out = 10 msec
Sample rate = 192 kHz
Bit depth = 16 (PCM)
Duration = 1 second per tone, 0.5 second intervals (4.5 seconds total file duration)

```{r tone}
#10 kHz tone
kHz_10 <- synth(f = 192000,
                cf = 10000,
                d = 1,
                a = 1,
                signal = "sine",
                output = "Wave"
                )

kHz_35 <- synth(f = 192000,
                cf = 35000,
                d = 1,
                a = 1,
                signal = "sine",
                output = "Wave"
                )

kHz_50 <- synth(f = 192000,
                cf = 50000,
                d = 1,
                a = 1,
                signal = "sine",
                output = "Wave"
                )

# 10 msec fade in and fade out
kHz_10 <- fadew(kHz_10, din = 0.010, dout = 0.010, shape = "exp", output = "Wave") 
kHz_35 <- fadew(kHz_35, din = 0.010, dout = 0.010, shape = "exp", output = "Wave")
kHz_50 <- fadew(kHz_50, din = 0.010, dout = 0.010, shape = "exp", output = "Wave")

#Add silence to each file
kHz_10 <- addsilw(kHz_10, at = "end", d = 0.5, output = "Wave")
kHz_35 <- addsilw(kHz_35, at = "end", d = 0.5, output = "Wave")
kHz_50 <- addsilw(kHz_50, at = "end", d = 0.5, output = "Wave")

#Join audio files
a <- pastew(kHz_35, kHz_10, output = "Wave")
puretones <- pastew(kHz_50, a, output = "Wave")

savewav(puretones, filename = "puretones_10_35_50kHz.wav") #final file save as .wav
```

## Oscillogram
``` {r oscillo}
oscillo(puretones)
```

## Power spectrum
``` {r powerspec}
meanspec(puretones,  wl = 1024)
```

## Spectrogram
``` {r spectrogram}
spectro(puretones,  wl = 1024)
```

##References
"WesternUS_Acoustic_Table_Mar2011" by Joe Szewczak, Humboldt State University Bat Lab, June 2018